Replicator-mutator and noise-perturbed replicator dynamics

### 2014-11-05 paper/paper_short.tex
results graphs merged

  \includegraphics[width=\textwidth]{plots/MeanMetrics.pdf}

  \caption{Means of recorded metrics for each triple of independent
    variables. Notice that the plots also show 95\% confidence
    intervals, but these are most often invisible, owing to the
    uniformity of outcomes across trials.}
  \label{fig:MeanMetrics}
\end{figure}

>>>>

  \includegraphics[width=\textwidth]{plots/MeanMetrics2.pdf}

  \caption{Means of gradient and proportions of categorical metrics for
    each triple of independent variables, with estimated 95\%
    confidence intervals.}
  \label{fig:MeanMetrics}
\end{figure}

### 2014-11-05 snippets/data_exploration/data_exploration_tmp.Rmd
results graphs merged

ds = data[,c("Number.of.states", "Impairment", "Tolerance", 
             "Speaker.entropy", "Hearer.entropy",
             "Speaker.informativity",
             "Speaker.Voronoiness", "Hearer.Voronoiness",
             "Expected.utility")]

@@

myLabeller <- function(var, value){
    value <- as.character(value)
    if (var=="variable") { 
        value[value=="Speaker.entropy"] <- "entropy sen"
        value[value=="Hearer.entropy"] <- "entropy rec"
        value[value=="Speaker.informativity"] <- "informativity"
        value[value=="Speaker.Voronoiness"] <- "Voronoiness sen"
        value[value=="Hearer.Voronoiness"] <- "Voronoiness rec"
        value[value=="Expected.utility"] <- "expected utility"
    }
    return(value)
}

pd <- position_dodge(.01)
mysize = 1.65
sp = ggplot(dsub, aes(x=Impairment, y=value, color = Number.of.states, shape=Number.of.states, linetype=Number.of.states)) + 
    geom_line(color="gray", position = pd) + xlab("imprecision") +
     geom_point(position = pd, size = mysize) +
     geom_errorbar(aes(ymin=value-ci, ymax=value+ci), width=0, position=pd) +
    scale_shape_discrete(name = "# states") +
    scale_linetype_discrete(name = "# states") +
    scale_color_discrete(name = "# states")

@@

ggsave(sp, file = "paper/plots/MeanMetrics.pdf", width=8, height = 8)

>>>>

data$converged = data$Iterations < 201
data$convex = data$Speaker.Convex.Cat

ds = data[,c("Number.of.states", "Impairment", "Tolerance", 
             "Speaker.entropy", "Hearer.entropy",
             "Speaker.Voronoiness", "Hearer.Voronoiness",
             "Expected.utility",
             "convex", "converged"
             )]

@@

myLabeller <- function(var, value){
    value <- as.character(value)
    if (var=="variable") { 
        value[value=="Speaker.entropy"] <- "entropy sen"
        value[value=="Hearer.entropy"] <- "entropy rec"
        value[value=="Speaker.Voronoiness"] <- "Voronoiness sen"
        value[value=="Hearer.Voronoiness"] <- "Voronoiness rec"
        value[value=="Expected.utility"] <- "expected utility"
    }
    return(value)
}

pd <- position_dodge(.01)
mysize = 1.65
sp = ggplot(dsub, aes(x=Impairment, y=value, color = Number.of.states, shape=Number.of.states, linetype=Number.of.states)) + 
    geom_line(color="gray", position = pd) + xlab("imprecision") +
     geom_point(position = pd, size = mysize) +
     geom_errorbar(aes(ymin=value-ci, ymax=value+ci), width=0, position=pd) +
    scale_shape_discrete(name = "# states", guide = guide_legend()) +
    scale_linetype_discrete(name = "# states", guide = guide_legend()) +
    scale_color_discrete(name = "# states", guide = guide_legend()) +
    theme(legend.position="top")

@@

ggsave(sp, file = "paper/plots/MeanMetrics2.pdf", width=8, height = 10)
